Interative Graphics
========================================================
Jennifer Chang

Starting Point
---------------
Use the code from last class to add a listener to a scatterplot of X and Y:
```{r}
install.packages("plumbr")
library(plumbr)
mf<-mutaframe(mtcars)
add_listener(mf,function(i,j){
  # i indicates the rows modified and j indicates columns
  plot(disp ~ mpg, data=as.data.frame(mf))
})

mf$disp<-sqrt(mf$disp)
```
Extend this setting to include a residual plot (in base plots you can set the number/layout of charts drawn with par(mfrow)).  Make also sure to show a fit of the current model (maybe by overlyaing the actual data)

Exercise
--------
Look at the package *stream* whcih contains methods for streaming data.  Stock market tickers, twitter posts, ... are examples of streaming data.  With streaming data you want to have some analysis fo the data as it comes in.  In manufacturing this might be to check the extremes, so that the materials are being produced within specifications, and the moment that it moves out a flag is thrown to pause the process and re-calibrate.

Real streaming data is hard to get - so we will be using streaming examples provided by the stream package.dsd <- DSD_GaussianMoving() creates 600 data points in two dimensions.  Watch to see how the stream behaves:

```{r}
install.packages("stream")
library(stream)
dsd<-DSD_GaussianMoving()
animate_data(dsd,600,xlim=c(-.2,1.2),ylim=c(-.2,1.2),pointInterval)
reset_stream(dsd)
```

Deliverable
---------
The function get_points allows you to get successive points from a data stream.  Generate a data stream with 10000 points.  Write a function that updates a mutaframe at regular intervals.  you may need to use Sys.sleep, and you will need ot decide on an appropriate interval size, and how many points to keep track of.

Add a listener function on the mutaframe that clusters the current batch of points (you should exclude old points after some time) using a k-means approach and plots a scatterplot of points coloured by cluster affiliation (how do you get colours to be stable?).

Bells and whistles: Find a way to appropriately and automaticaly decide between 2 and 3 clusters.
